% !Mode:: "TeX:UTF-8"
\thispagestyle{empty}
\renewcommand{\baselinestretch}{1.5}  %下文的行距

\begin{cnabstract}
利用VC6.0开发工具开发一个图书管理系统系统。系统实现的功能模块有：用户登录、用户注册、数据库读取、数据库查询、借书、还书、查询书和升级权限的功能。
该系统的特色是轻量型和易开发，同时又有高可移植性的特点。系统操作实现的功能比较完善，人机界面实现简单，达到操作过程中的直观、方便、实用、安全等要求。系统具有一定的实用性。
实现了图书管理信息系统的图书检索、借阅管理、统计报表管理、图书个性化推荐等功能,能够有效提升图书馆的智能化信息管理和个性化信息服务水平。
\end{cnabstract}
\par
\vspace*{2em}

\cnkeywords{图书管理系统; 推荐系统; 信息管理}


%%====英文摘要==========================%


\begin{enabstract}
Using VC6.0 development tool to develop a library management system. The functional modules implemented by the system include: user login, user registration, database reading, database query, borrowing, returning, querying and upgrading permissions.

The system is characterized by light weight, easy development and high portability. The functions of the system operation are relatively perfect, and the realization of man-machine interface is simple, so as to meet the requirements of intuition, convenience, practicality and safety in the operation process. The system has certain practicability.

It realizes the functions of book retrieval, borrowing management, statistical report management and Book personalized recommendation of the library management information system, and can effectively improve the intelligent information management and personalized information service level of the library.
\end{enabstract}
\par
\vspace*{2em}
\enkeywords{Book Manage System;Recommend System;Information Management}
%%%%%-- Key words --------------------------------------%%%%%%%
%%%%-- 注意: 每个关键词之间用“；”分开，最后一个关键词不打标点符号